LSOA domestic Electricty and Gas maps

### 2021-09-02 LSOA domestic Elec and Gas.Rmd
fixed % change plots and added an example by facet_wrap

head(df)
Solent <- dplyr::filter(df, `Local Authority Name.x` == "Basingstoke and Deane"|
                           `Local Authority Name.x` == "East Hampshire"|
                           `Local Authority Name.x` == "Eastleigh"|
                           `Local Authority Name.x` == "Fareham"|
                           `Local Authority Name.x` == "Gosport"|
                           `Local Authority Name.x` == "Hart"|
                           `Local Authority Name.x` == "Havant"|
                           `Local Authority Name.x` == "New Forest"|
                           `Local Authority Name.x` == "Portsmouth"|
                           `Local Authority Name.x` == "Rushmoor"|
                           `Local Authority Name.x` == "Southampton"|
                           `Local Authority Name.x` == "Test Valley"|
                           `Local Authority Name.x` == "Winchester"|
                           `Local Authority Name.x` == "Isle of Wight"
                           )

ggplot(Solent,aes(x =as.factor(IMD_Decile)), y =(de_diff/de2010), colour =as.factor(IMD_Decile), group =IMD_Decile) +  geom_boxplot()

>>>>

head(df)
Solent <- dplyr::filter(df, `Local Authority Name.x` == "Basingstoke and Deane"|
                           `Local Authority Name.x` == "East Hampshire"|
                           `Local Authority Name.x` == "Eastleigh"|
                           `Local Authority Name.x` == "Fareham"|
                           `Local Authority Name.x` == "Gosport"|
                           `Local Authority Name.x` == "Hart"|
                           `Local Authority Name.x` == "Havant"|
                           `Local Authority Name.x` == "New Forest"|
                           `Local Authority Name.x` == "Portsmouth"|
                           `Local Authority Name.x` == "Rushmoor"|
                           `Local Authority Name.x` == "Southampton"|
                           `Local Authority Name.x` == "Test Valley"|
                           `Local Authority Name.x` == "Winchester"|
                           `Local Authority Name.x` == "Isle of Wight"
                           )
head(Solent)
ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =100*(de_diff/de2010), 
                   group = IMD_Decile,
                   colour = IMD_Decile)) +  
  geom_boxplot() +
  scale_color_continuous(name = "IMD Decile") + # rename the legend scale
  labs(x = "IMD Decile",
       y = "% change")

# or without colour but using facets for Local Authorities
ggplot(Solent, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =100*(de_diff/de2010), 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "% change") +
  facet_wrap(`Local Authority Name.x` ~ .)
